Spatial Reasoning and Data Displays

### 2015-03-16 Paper/InfoVis2015/appendix.tex
InfoVis style file submission

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

<<pca,echo=F, warning=F, message=F,include=F>>=
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
pca2 <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
# screeplot(pca)
@
<<pcasummary5,echo=F,include=F>>=
print(xtable(summary(pca), caption="Importance of principal components, analyzing all five tests.\\label{tab:PCAvariance5}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, size="footnotesize", table.placement="ht", caption.placement="top")
@

<<pcarotation5,echo=F,include=F>>=
print(xtable(pca$rotation, caption="PCA Rotation matrix for all five tests. The first principal component is essentially an average of all five tests. 
             \\label{tab:PCArotation5}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, table.placement="ht", caption.placement="top")
@

<<linearmodel, include=FALSE, echo=FALSE>>=
pca2 <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
ans.model <- data.frame(ans.summary, data.frame(pca2$x))
# exclude all variables that are not supposed to go into the linear model
# those are the unrotated tests; instead we have the PCs
excl <- c("id", "card_rot", "fig_class", "folding", "vis_search", "vidgame_hrs", "major1", "major2", "minor1", "minor2", "learning_disability", "colorblind", "epilepsy", "normal_vision")

ans.model$math_science_research <- ans.model$math_science_research=="y"
ans.model$stats_class <- ans.model$stats_class=="y"
ans.model$calc_1 <- ans.model$calc_1=="y"
pcmath <- prcomp(ans.model[,c("math_science_research", "stats_class", "calc_1", "math_skills", "stem")], scale=T)
pcmath$rotation
# first component of math PCA is average of math_skills, calc_1 and stem
# second component is stat_class and research

#biplot(pcmath)
#biplot(pcmath, 3:4)

xtabs(~stem+sex, data=ans.model)
# sad day!

xtabs(~stem+calc_1, data=ans.model)
# stem major is more associated with performance on lineups than calc 1...

xtabs(~stats_class+math_science_research, data=ans.model)
# only one kid is doing research without a stats class

# recode to sum of them
ans.model$STATS <- with(ans.model, stats_class + math_science_research)
ans.model$MATH <- with(ans.model, calc_1+math_skills/5+stem)

excl <- c(excl, c("math_science_research", "stats_class"))
excl <- c(excl, c("calc_1", "math_skills", "stem"))
incl <- setdiff(names(ans.model), excl)

m0 <- lm(lineup~., data=ans.model[, incl])

# use AIC in backward selection
library(MASS)
m1 <- stepAIC(m0, direction="both")
@
<<lineupblockpca, echo=F, include=F, warning=F, message=F, fig.width=6, fig.height=4>>=
lineup.block.pca <- prcomp(lineup.section.summary[,c("lineup_1", "lineup_2", "lineup_3", "card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
rotation <- melt(lineup.block.pca$rotation)
importance <- as.data.frame(summary(lineup.block.pca)$importance)[2,]
rotation <- merge(rotation, melt(importance, variable.name="Var2", value.name="importance"))
rotation$Var1 <- factor(rotation$Var1, 
                        levels=c("vis_search", "folding", "card_rot", "fig_class", "lineup_3", "lineup_2", "lineup_1"),
                        labels=c("Visual Search", "Paper Folding", "Card Rotation", "Figure Class.", "Lineup Test 3", "Lineup Test 2", "Lineup Test 1"))

@

@@

Substituting in the provided numbers, we get
\begin{align*}
\mu_{\text{all}} &= \left(323\!\cdot\!114.9\! +\! 294\!\cdot\!120.0\right)/(323\!+\!294) \\
& = \Sexpr{round((120.0*294 + 114.9*323)/617/2, 1)}\\
\sigma_{\text{all}} &= \sqrt{\left(323 \cdot 27.8^2 \!+\! 294 \cdot 30^2\right)/(323\!+\!294)} \\
& = \Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617)/2, 1)}.
\end{align*}

@@

\section{Lineup Performance and Demographic Characteristics}\label{app:categoricalresults}
Table~\ref{tab:ttest-demographics} provides the results of a sequence of linear models fit to the lineup data. Each row in the table represents a single model, with one predictor variable (a factor with two or more levels). Due to sample size considerations, multiple testing corrections were not performed; in addition, the independent variables are correlated: in our sample, males are more likely to have completed Calculus 1, but are also more likely to spend time playing video games. As such, a model including two or more of the significant predictor variables shows all included variables to be nonsignificant. To better understand the effects of these variables, a larger study is necessary. 
<<ttests.categ, echo=F, eval=T, results='asis'>>=
tmp <- dlply(lineup.summary.categorical, .(variable), function(df){
    tmp <- anova(lm(lineup~factor(value, ordered=F), data=df))
    coefs <- as.data.frame(tmp)[1,]
    coefs$level <- gsub("factor(value, ordered = F)", unique(df$variable), rownames(coefs), fixed=T)
    rownames(coefs) <- NULL
    coefs <- coefs[,c(6, 1:5)]
    names(coefs) <- c("Variable", "DF", "Sum.of.Squares", "Mean.Squared", "F.value", "p.value")
    coefs
})

tmp <- rbind.fill(tmp)
tmp <- tmp[order(tmp$p.value, decreasing=F),]

lineup.summary.categorical$variable <- factor(lineup.summary.categorical$variable, levels=unique(tmp$Variable))
lineup.summary.categorical$value <- factor(lineup.summary.categorical$value, levels=c("0","1", "2","3","4","5","[1, 2)", "[2, 5)", "5+", "18-20", "21+", "TRUE", "FALSE", "Female", "Male"))

tmp <- dlply(lineup.summary.categorical, .(variable), function(df){
    tmp <- anova(lm(lineup~factor(value, ordered=F), data=df))
    coefs <- as.data.frame(tmp)[1,]
    coefs$level <- gsub("factor(value, ordered = F)", unique(df$variable), rownames(coefs), fixed=T)
    rownames(coefs) <- NULL
    coefs <- coefs[,c(6, 1:5)]
    names(coefs) <- c("Variable", "DF", "Sum.of.Squares", "MeanSq", "F", "p.val")
    coefs
})

tmp <- rbind.fill(tmp)
tmp2 <- tmp[order(tmp$p.val, decreasing=F),-3]
tmp2$Variable <- gsub("Math/Science", "STEM", gsub(" Experience", "", gsub(" Hrs/Wk", " hrs", tmp2$Variable)), fixed=T)
print(xtable(tmp2, digits=c(1, 1, 0, 3, 2, 3), caption="Participant demographics' impact on lineup score. The table below shows each single demographic variable's association with lineup score. STEM major, completion of Calculus I, time spent playing video games, and gender all show some association with score on statistical lineups. \\label{tab:ttest-demographics}"), include.rownames=F, floating.environment="table", caption.placement="top")
@

@@

<<pcasummary4,echo=F, results='asis'>>=
pca2 <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
print(xtable(summary(pca2), caption="Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\\label{tab:PCAvariance4}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, size="footnotesize", table.placement="htb", caption.placement="top")
@
Table~\ref{tab:PCAvariance4} contains the proportion of the variance in the four cognitive tasks represented by each principal component. PC1 accounts for about \Sexpr{round(summary(pca2)$importance[3,1],1)*100}\% of the variance; Figure~\ref{fig:biplots4} and Table~\ref{tab:PCArotation4} confirm that PC1 is a measure of the similarity between all 4 tests; that is, a participant's general (or visual) aptitude. PC2 differentiates the figure classification test from the visual searching test, while PC3 differentiates these two from the paper folding test. PC4 is not particularly significant (it accounts for \Sexpr{round(summary(pca2)$importance[2,4]*100,1)}\% of the variance), but it differentiates the card rotation task from the paper folding task.

<<pcarotation4,echo=F, results='asis'>>=
print(xtable(pca2$rotation, caption="Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\\label{tab:PCArotation4}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, table.placement="htb", caption.placement="top")
@

<<biplot-pca4, fig.cap="", fig.width=4.5, fig.height=4.5, warning=F, message=F, out.width='.7\\linewidth', comment="|", fig.cap="Biplots of principal components 1-4 with observations. Principal component analysis was performed on the four cognitive tests used to understand the association between the cognitive skills required for these tests and the skills required for the lineup protocol.  \\label{fig:biplots4}", echo=F, fig.env="figure">>=
par(mar=c(4,4,.1,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
biplot(pca2, choices=1:2, pc.biplot=T, cex=c(.5, 1), xlim=c(-2.5,2.5), ylim=c(-2.5,2.5))
biplot(pca2, choices=3:4, pc.biplot=T, cex=c(.5, 1), xlim=c(-3,3), ylim=c(-2.5,2.5))
@
Figure~\ref{fig:biplots4} shows that the first PC does not differentiate between any of the tasks; it might be best understood as a general aptitude factor. All of the remaining principal components distinguish between the cognitive tasks; 
PC2 and PC3 separate  paper folding from visual search and from the lineup and figure classification tasks, while PC4 and PC5 mainly separate lineups from card rotation and figure classification. This separation allows us to compare the tasks which are similar from among the principal components. 
According to Table~\ref{tab:PCArotation4}, the first three principal components account for \Sexpr{round(summary(pca2)$importance[3,3]*100,1)}\% of the variance.

@@

<<biplots-pca5, fig.cap="", fig.width=4.5, fig.height=4.5, warning=F, message=F, out.width='.7\\linewidth', comment="|", fig.cap="Biplots of principal components 2-5 with observations. The lineup task appears to be most similar to the figure classification task, based on the plot of PC2 vs. PC3.  \\label{fig:biplots5}", echo=F, fig.env="figure">>=
par(mar=c(4,4,.1,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
biplot(pca, choices=2:3, pc.biplot=T, cex=c(.5, 1), xlim=c(-2.5,2.5), ylim=c(-2.5,2.5))
biplot(pca, choices=4:5, pc.biplot=T, cex=c(.5, 1), xlim=c(-2,2), ylim=c(-2,2))
@

@@

<<lineup-types,echo=F, fig.width=4, fig.height=8, include=F, warning=F, message=F>>=
lineup.type.sum2$plot.type <- str_replace(lineup.type.sum2$plot.type, "rotated", "rot")
lineup.type.sum2$plot.type <- str_replace(as.character(lineup.type.sum2$plot.type), "error", "err")
lineup.type.sum2$plot.type <- factor(lineup.type.sum2$plot.type, 
                                     levels=c("violinplot", "jitter.boxplot", "bee.swarm.boxplot", "boxplot", 
                                              "scatterplot", "density", "histogram", 
                                              "qq.line", "qq.line.err", "qq.line.err.rot"), 
                                     labels=c("Violin Plot", "Boxplot + Points", "Bee Swarm Boxplot", "Boxplot", 
                                              "Scatterplot", "Density Plot", "Overlaid Histogram", 
                                              "QQ-plot + Line", "QQ-plot +\nAcceptance Band", 
                                              "Rotated QQ-plot +\nAcceptance Band")
                                     )
loadfonts()
qplot(data=subset(lineup.type.sum2, !is.na(plot.type)& testtype=="lineup"), 
      x=score, y=..scaled.., colour=factor(testnum), geom="density", cut=4) + 
  facet_wrap(~plot.type, ncol=2) + 
  xlab("Proportion of Lineups Correct") + 
  ylab("Density") + 
  geom_vline(aes(xintercept=0), linetype=3) + 
  scale_colour_discrete("Lineup Test Number") + 
  scale_x_continuous(breaks=c(-.33, 0, .33, .67, 1)) +
  scale_y_continuous(breaks=c(0, .5, 1)) +
  theme_bw() + 
  theme(legend.position="bottom", legend.direction="horizontal", 
        axis.text.x=element_text(angle=30, hjust=1),
        plot.margin=unit(c(0,0,0,0),"mm"), 
        axis.ticks.y=element_blank(), axis.text.y=element_blank())
embedFonts("./Figure/fig-lineup-types-1.pdf")
@

@@

<<lineup-types-scores,echo=F,fig.width=6, fig.height=12, include=F, warning=F, message=F>>=
lineup.type.sum3 <- dcast(lineup.type.sum2, id + testtype ~ plot.type, value.var="score", fun.aggregate = mean)
other.scores <- subset(lineup.type.sum3, testtype!="lineup")[,c(1,2,13)]
names(other.scores)[3] <- "testscore"
lineup.scores <- melt(subset(lineup.type.sum3, testtype=="lineup")[,c(1,3:12)], id.vars = 1)
names(lineup.scores)[2:3] <- c("lineup.type", "lineup.pct")
lineup.type.sum3 <- merge(other.scores, lineup.scores, all.x=T, all.y=T)
lineup.type.sum3$lineup.type <- factor(lineup.type.sum3$lineup.type, 
                                     levels=c("Violin Plot", "Boxplot + Points", "Bee Swarm Boxplot", "Boxplot", 
                                              "Scatterplot", "Density Plot", "Overlaid Histogram", 
                                              "QQ-plot + Line", "QQ-plot +\nAcceptance Band", 
                                              "Rotated QQ-plot +\nAcceptance Band"), 
                                     labels=c("Violin Plot", "Boxplot\n + Points", "Bee Swarm \nBoxplot", "Boxplot", 
                                              "Scatter\nPlot", "Density\nPlot", "Overlaid\nHistogram", 
                                              "QQ-plot\n+ Line", "QQ-plot\n+ Bands", 
                                              "Rotated QQ\nplot + Bands")
                                     )

cor.labels <- ddply(lineup.type.sum3, .(lineup.type, testtype), summarize, x=min(testscore), y=max(lineup.pct), label=paste0("cor = ", round(cor(testscore, lineup.pct), 2)))
loadfonts()
qplot(data=subset(lineup.type.sum3, testtype!="vis_search"), 
      x=testscore, y=lineup.pct, geom=c("smooth", "jitter"), colour=I("grey30"), method="lm") + 
  facet_grid(lineup.type~testtype, scales="free_x") + 
  ylab("Scaled Lineup Score") + 
  xlab("Test Score")+
  geom_text(data=subset(cor.labels, testtype!="vis_search"), aes(x=x, y=1, label=label), hjust=0, vjust=1, size=3) + 
  theme_bw() + 
  theme(legend.position="bottom", legend.direction="horizontal", 
        axis.text.x=element_text(angle=30, hjust=1),
        plot.margin=unit(c(0,0,0,0),"mm"))
embedFonts("./Figure/fig-lineup-types-scores-1.pdf")
@
\begin{figure}[ht]
\includegraphics[width=\linewidth]{Figure/fig-lineup-types-scores-1}
\caption{Scatterplots of scaled lineup scores by aptitude test scores. There is some indication that different types of lineup tasks may utilize different visual skills; for instance, QQ-plots with confidence bands may require more skill at mental rotation than QQ-plots without the bands. \label{fig:scatterplottypes}}
\end{figure}

For comparison, the correlation between general lineup score (non-subdivided) and the card rotation test score was \Sexpr{sprintf("%.3f", cor(ans.summary$lineup, ans.summary$card_rot))}, the correlation between general lineup score and the figure classification test was \Sexpr{sprintf("%.3f", cor(ans.summary$lineup, ans.summary$fig_class))}, and the correlation between lineup score and the paper folding test was \Sexpr{sprintf("%.3f", cor(ans.summary$lineup, ans.summary$folding))}.While we can compare the correlation strength between tasks, it is clear that the correlation between the score on any single lineup type and a particular visual aptitude score is lower than the overall relationship that we attribute to visual ability. Additional data is imperative to understand the reasoning required for specific types of plots - it is likely that the 5-10 trials per participant presented in each chart in Figure~\ref{fig:scatterplottypes} are simply not sufficient to uncover any specific relationship between reasoning ability and lineup task.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

Substituting in the provided numbers, we get
\begin{align*}
\mu_{\text{all}} &= \left(323\!\cdot\!114.9\! +\! 294\!\cdot\!120.0\right)/(323\!+\!294) \\
& = 58.7\\
\sigma_{\text{all}} &= \sqrt{\left(323 \cdot 27.8^2 \!+\! 294 \cdot 30^2\right)/(323\!+\!294)} \\
& = 14.4.
\end{align*}

@@

\section{Lineup Performance and Demographic Characteristics}\label{app:categoricalresults}
Table~\ref{tab:ttest-demographics} provides the results of a sequence of linear models fit to the lineup data. Each row in the table represents a single model, with one predictor variable (a factor with two or more levels). Due to sample size considerations, multiple testing corrections were not performed; in addition, the independent variables are correlated: in our sample, males are more likely to have completed Calculus 1, but are also more likely to spend time playing video games. As such, a model including two or more of the significant predictor variables shows all included variables to be nonsignificant. To better understand the effects of these variables, a larger study is necessary. 
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{| Error in eval(expr, envir, enclos): contrasts can be applied only to factors with 2 or more levels}}\end{kframe}% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[ht]
\centering
\caption{Participant demographics' impact on lineup score. The table below shows each single demographic variable's association with lineup score. STEM major, completion of Calculus I, time spent playing video games, and gender all show some association with score on statistical lineups. \label{tab:ttest-demographics}} 
\begin{tabular}{lrrrr}
  \hline
Variable & DF & Mean.Squared & F.value & p.value \\ 
  \hline
stem & 1 & 401.517 & 14.44 & 0.001 \\ 
  calc\_1 & 1 & 204.569 & 6.15 & 0.018 \\ 
  vidgame\_hrs\_factor & 3 & 108.847 & 3.44 & 0.028 \\ 
  sex & 1 & 140.844 & 4.02 & 0.053 \\ 
  art\_skills & 4 & 75.891 & 2.28 & 0.082 \\ 
  verbal\_skills & 3 & 60.220 & 1.68 & 0.191 \\ 
  math\_science\_research & 1 & 59.670 & 1.60 & 0.214 \\ 
  AutoCAD & 1 & 50.893 & 1.36 & 0.252 \\ 
  age & 1 & 34.434 & 0.91 & 0.348 \\ 
  math\_skills & 3 & 37.039 & 0.98 & 0.416 \\ 
  stats\_class & 1 & 9.062 & 0.23 & 0.631 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[htb]
\centering
\caption{Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\label{tab:PCAvariance4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Standard deviation & 1.61 & 0.81 & 0.73 & 0.49 \\ 
  Proportion of Variance & 0.64 & 0.16 & 0.13 & 0.06 \\ 
  Cumulative Proportion & 0.64 & 0.81 & 0.94 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

Table~\ref{tab:PCAvariance4} contains the proportion of the variance in the four cognitive tasks represented by each principal component. PC1 accounts for about 60\% of the variance; Figure~\ref{fig:biplots4} and Table~\ref{tab:PCArotation4} confirm that PC1 is a measure of the similarity between all 4 tests; that is, a participant's general (or visual) aptitude. PC2 differentiates the figure classification test from the visual searching test, while PC3 differentiates these two from the paper folding test. PC4 is not particularly significant (it accounts for 5.9\% of the variance), but it differentiates the card rotation task from the paper folding task.

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[htb]
\centering
\caption{Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\label{tab:PCArotation4}} 
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
card.rot & 0.55 & -0.19 & -0.38 & 0.72 \\ 
  fig.class & 0.46 & 0.58 & 0.66 & 0.14 \\ 
  folding & 0.52 & 0.33 & -0.53 & -0.59 \\ 
  vis.search & 0.46 & -0.72 & 0.38 & -0.34 \\ 
   \hline
\end{tabular}
\end{table}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}

{\centering \includegraphics[width=.7\linewidth]{Figure/fig-biplot-pca4-1} 
\includegraphics[width=.7\linewidth]{Figure/fig-biplot-pca4-2}

}

\caption{Biplots of principal components 1-4 with observations. Principal component analysis was performed on the four cognitive tests used to understand the association between the cognitive skills required for these tests and the skills required for the lineup protocol.  \label{fig:biplots4}}\label{fig:biplot-pca4}
\end{figure}

\end{knitrout}
Figure~\ref{fig:biplots4} shows that the first PC does not differentiate between any of the tasks; it might be best understood as a general aptitude factor. All of the remaining principal components distinguish between the cognitive tasks; 
PC2 and PC3 separate  paper folding from visual search and from the lineup and figure classification tasks, while PC4 and PC5 mainly separate lineups from card rotation and figure classification. This separation allows us to compare the tasks which are similar from among the principal components. 
According to Table~\ref{tab:PCArotation4}, the first three principal components account for 94.1\% of the variance.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}

{\centering \includegraphics[width=.7\linewidth]{Figure/fig-biplots-pca5-1} 
\includegraphics[width=.7\linewidth]{Figure/fig-biplots-pca5-2}

}

\caption{Biplots of principal components 2-5 with observations. The lineup task appears to be most similar to the figure classification task, based on the plot of PC2 vs. PC3.  \label{fig:biplots5}}\label{fig:biplots-pca5}
\end{figure}

\end{knitrout}

@@

@@

\begin{figure}[ht]
\includegraphics[width=\linewidth]{Figure/fig-lineup-types-scores-1}
\caption{Scatterplots of scaled lineup scores by aptitude test scores. There is some indication that different types of lineup tasks may utilize different visual skills; for instance, QQ-plots with confidence bands may require more skill at mental rotation than QQ-plots without the bands. \label{fig:scatterplottypes}}
\end{figure}

For comparison, the correlation between general lineup score (non-subdivided) and the card rotation test score was 0.505, the correlation between general lineup score and the figure classification test was 0.512, and the correlation between lineup score and the paper folding test was 0.471.While we can compare the correlation strength between tasks, it is clear that the correlation between the score on any single lineup type and a particular visual aptitude score is lower than the overall relationship that we attribute to visual ability. Additional data is imperative to understand the reasoning required for specific types of plots - it is likely that the 5-10 trials per participant presented in each chart in Figure~\ref{fig:scatterplottypes} are simply not sufficient to uncover any specific relationship between reasoning ability and lineup task.
